### 2008-09-24 trunk/Latex/H2Preview/H2PrevConcs.tex

>>>>

========================

A MATLAB Preview Control toolbox, for the given algorithm and its $\hinf$ counterpart, can be obtained from: %\url{http://www3.imperial.ac.uk/controlandpower/research/portfoliopartnership/projects/preview_control}
\url{http://code.google.com/p/preview-control-toolbox/}, where the first author's thesis may also be found.

### 2008-09-24 trunk/Latex/H2Preview/H2PrevOF.tex

It is well known that the $\htwo$-optimal controller has an observer structure. If $w=0$, then the observer will contain an exact copy of the states of $G$ and $W_r$ (once intial transients have decayed). Therefore the closed-loop transfer function $T_{r\rightarrow z}$ will be precisely the same as that that results from application of the full information controller, $K_{FI}$ to the plant $P_{FI}$. Remark~\ref{rem:FIminwandr} implies that the value of $\nrm{T_{r\rightarrow z}}_2$ achieved by the this controller is indeed minimal.
\end{pf}

>>>>

It is well known that the $\htwo$-optimal controller has an observer structure. If $w=0$, then the observer will contain an exact copy of the states of $G$ and $W_r$ (once intial transients have decayed). Therefore the closed-loop transfer function $T_{r\rightarrow z}$ will be precisely the same as that resulting from application of the full information controller, $K_{FI}$ to the plant $P_{FI}$. Remark~\ref{rem:FIminwandr} implies that the value of $\nrm{T_{r\rightarrow z}}_2$ achieved by the this controller is indeed minimal.
\end{pf}
